%% ---------------------------------------------------------------
%% biblatex-chem --- A set of biblatex implementations of
%%   chemistry-related bibliography styles
%% Maintained by Joseph Wright
%% E-mail: joseph.wright@morningstar2.co.uk
%% Released under the LaTeX Project Public License v1.3c or later
%% See http://www.latex-project.org/lppl.txt
%% ---------------------------------------------------------------
%%  

\documentclass[a4paper]{ltxdoc}
\usepackage[T1]{fontenc}
\usepackage[style=chem-rsc]{biblatex}
\usepackage[final]{microtype}
\usepackage{csquotes,lmodern}
\usepackage{hyperref}

\hypersetup{pdfborder = 0 0 0}

\addbibresource{biblatex-chem.bib}

\author{Joseph Wright\thanks{E-mail: 
  \href{mailto:joseph.wright@morningstar2.co.uk}
  {\texttt{joseph.wright@morningstar2.co.uk}}}}
\title{The \pkg{chem-rsc} bibliography style for \pkg{biblatex}%
  \footnote{This file describes v1.1a, last revised 2011/08/16.}}
\date{Released 2011/08/16}

\providecommand*\opt[1]{\texttt{#1}}
\providecommand*\pkg[1]{\textsf{#1}}

\let\DescribeOption\DescribeEnv

\RecordChanges

\begin{document}

\maketitle

This package provides a style for \pkg{biblatex} which follows the
guidelines of Royal Society of Chemistry. The citation style is numeric
and unsorted. The bibliography style follows the pattern of the layout
used in the journal \emph{Chemical Communications}. The style should be
loaded in the usual way
\begin{verbatim}
\usepackage[style=chem-rsc]{biblatex}
\end{verbatim}
The References section of this document demonstrates the format 
generated by the package using the \texttt{biblatex-chem.bib} database
of example citations.

\DescribeOption{doi}
\DescribeOption{url}
The standard \opt{doi} and \opt{url} options for bibliographies are supported
by \texttt{chem-rsc}, but as standard are set \opt{false}.

\DescribeOption{articletitle}
The use of article titles varies between individual journals. The
boolean option \opt{articletitle} is available is control this behaviour,
and is set \opt{false} as standard.

\DescribeOption{chaptertitle}
The option boolean \opt{chaptertitle} option is provided to allow flexibility
for the inclusion of chapter titles for \texttt{inbook} and \texttt{incollection}
entries. The standard setting leaves this option off.

\DescribeOption{pageranges}
The use of full page ranges varies between journals and indeed between
different papers in individual journals. The \opt{pageranges} boolean option
is available to turn on and off printing of full page ranges, thus allowing
printing of only the first page even when the database contains the full
page range. This option is set \opt{true} as standard.

Suggestions for improvement and bug reports can be logged in the package
issue database, found at
\url{https://bitbucket.org/josephwright/biblatex-chem/issues}, or can
be sent by e-mail to 
\href{mailto:joseph.wright@morningstar2.co.uk}
  {\texttt{joseph.wright@morningstar2.co.uk}}.

\nocite{*}

\printbibliography

\changes{v1.0}{2010/11/20}{First stable release}
\changes{v1.0a}{2010/12/22}{Format \enquote{\emph{et al.}}~in italics
  when using \texttt{chem-rsc} style}
\changes{v1.0b}{2011/01/10}{Require \pkg{biblatex} v1.1}
\changes{v1.0b}{2011/01/10}{Use new \texttt{maxbibnames} option such
  that bibliographies print all authors but citations use truncated
  lists when necessary}
\changes{v1.0c}{2011/01/11}{Add version history for stable releases}
\changes{v1.0d}{2011/01/17}{Corrections for formatting of
  optionally-included article and chapter titles}
\changes{v1.0d}{2011/01/17}{Include additional punctuation tracker
  corrections for non-English bibliographies}
\changes{v1.1}{2011/08/15}{Styles revised to work with \pkg{biblatex} v1.6}
\changes{v1.1a}{2011/08/16}{Turn off standard \opt{url} option by default}
\changes{v1.1a}{2011/08/16}{Reintroduce \opt{chaptertitle} option}

\PrintChanges

\end{document}

%% 
%% Copyright (C) 2010,2011 by
%%   Joseph Wright <joseph.wright@morningstar2.co.uk>
%% 
%% It may be distributed and/or modified under the conditions of
%% the LaTeX Project Public License (LPPL), either version 1.3c of
%% this license or (at your option) any later version.  The latest
%% version of this license is in the file:
%% 
%%    http://www.latex-project.org/lppl.txt
%% 
%% This work is "maintained" (as per LPPL maintenance status) by
%%   Joseph Wright.
%% 
%% This work consists of the files biblatex-chem.bib,
%%                                 biblatex-chem.tex,
%%                                 biblatex-chem-acs.tex,
%%                                 biblatex-chem-angew.tex,
%%                                 biblatex-chem-biochem.tex,
%%                                 biblatex-chem-rsc.tex,
%%                                 chem-acs.bbx,
%%                                 chem-acs.cbx,
%%                                 chem-angew.bbx,
%%                                 chem-angew.cbx,
%%                                 chem-biochem.bbx,
%%                                 chem-biochem.cbx,
%%                                 chem-rsc.bbx and
%%                                 chem-rsc.cbx,
%%           and the derived files biblatex-chem.pdf and
%%                                 biblatex-chem-acs.pdf,
%%                                 biblatex-chem-angew.pdf,
%%                                 biblatex-chem-biochem.pdf,
%%                                 biblatex-chem-rsc.pdf.
%% 
%%
%% End of file `biblatex-chem-rsc.tex'.